Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
private future region relation

\subsection{Worlds}
% Intuition worlds
The worlds are step-indexed Kripke worlds. For the reader not familiar
with these, it is sufficient to think of worlds as finite sets of
regions.

@@

\subsubsection{Future worlds}
There are two future world relations a \emph{public future world} relation and a \emph{private future world} relation. In both future world relations, we have extension ordering, so a future world $W'$ of $W$ has at least the same regions as $W$, but it may add new regions imposing new protocols on part of the memory. The two future world relations differ in the way existing regions are allowed to evolve. In a \emph{public future region} 
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

{\bf Public future regions}
The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

{\bf Private future regions}
The \emph{private future} region relation satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}

The two future world relations satisfy the following properties: They allow for any extension of the current world and all existing worlds are allowed to move to an appropriate future region. That is

>>>>

\subsection{Worlds}
\todo[inline]{Find a good place to describe monotonicity of
  interpretation function.}
% Intuition worlds
The worlds are step-indexed Kripke worlds. For the reader not familiar
with these, it is sufficient to think of worlds as finite sets of
regions that impose protocols on the memory.

@@

\subsubsection{Future worlds}
In order to model changes to memory over time, we use the future world
relations. The future world relations model how more memory may be
allocated but also how memory may change. How memory is allowed to
change over time depends on the region that governs it and the future
world relation used. The most interesting part about the future worlds
is how it affects the regions, so we first look at the properties of
the \emph{public future region} relation and the \emph{private future
  region} relation. We then use these relations to describe the future
world relations.

{\bf Private future regions}
In the private future region relation, we allow revocation of $\temp$
regions. The regions cannot be revoked by removing them from the
world, because we need the future world relations to be
monotone. This is why we have the $\revoked$ region, so we have
a region that can serve as a mask. We can, however, let any region
serve as a mask, so in the private future region relation, we allow a
$\temp$ region to become any valid region. As the $\revoked$ region
serves as a mask, we let any valid region take its place in the
private future region relation.

If a $\temp$ region is not masked by a region, then it behaved like a
$\perm$ region. The $\perma$ regions stay the same type and they are
allowed to take a transition in the private part of the transition
system. Which can be thought of as the memory changes according to
some protocol.

The properties of the \emph{private future region} relation are:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}

{\bf Public future regions}
The public future regions relation has the following properties:
% - permanent and temporary regions stay the same type
% - public transitions
The $\perma$ and $\temp$ regions stay the same type of region and they
are allowed to take a transition in the public part of their
transition systems.

% - revoked regions can be reused as temporary regions
The $\revoked$ regions can either stay $\revoked$, or they can become
any $\temp$ region. When a region is $\revoked$ it serves as a mask
for a revoked $\temp$ region. We use masks rather than deleting the
region altogether for monotonicity reasons, but we might as well let a
new $\temp$ region serve as the mask. We do not allow $\revoked$
regions to become a $\perma$ region because we want the private future
region relation to be able to reuse any region it has revoked.

The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

% The future world relation are really the ones from thm, the above
% are properties of them.
{\bf Future world relations}
There are two future world relations a \emph{public future world}
relation and a \emph{private future world} relation. In both future
world relations, we have extension ordering, so a future world $W'$ of
$W$ has at least the same regions as $W$, but $W'$ may have new regions
imposing new protocols on parts of the memory. The two future world
relations differ in the way existing regions are allowed to evolve. In
a \emph{public future world}, the regions are allowed to evolve
according to the \emph{public future region} relation. In a
\emph{private future world}, the regions are allowed to evolve
according to the \emph{private future world} relation. The future
world relations are defined as follows:
\begin{mathpar}
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurewk W(r) }
  { W' \futurewk W }
  \and
  \inferrule{ \dom(W') \supseteq \dom(W)\\ 
    \forall r \in \dom(W) \ldotp W'(r) \futurestr W(r) }
  { W' \futurestr W }
\end{mathpar}

% Relate to STSs for high-level languages. Have the public-private
% transitions, but they are also used for more than this
